\hypertarget{problem-7-uniform-lattice-with-2-torsion-and-rationally-acyclic-universal-cover}{%
\section{Problem 7: Uniform Lattice with 2-Torsion and Rationally Acyclic Universal Cover}\label{problem-7-uniform-lattice-with-2-torsion-and-rationally-acyclic-universal-cover}}

\hypertarget{problem-statement}{%
\subsection{Problem Statement}\label{problem-statement}}

Suppose \(\Gamma\) is a uniform lattice in a real semisimple Lie group, and
\(\Gamma\) contains an element of order \texttt{2}. Is it possible that \(\Gamma\) is the
fundamental group of a closed manifold whose universal cover is acyclic over
\texttt{Q}?

\hypertarget{status-in-this-writeup}{%
\subsection{Status in This Writeup}\label{status-in-this-writeup}}

\textbf{Answer: yes} (via the rotation route; closed in this branch via the standard codim-2 surgery theorem chain).

\begin{itemize}
\tightlist
\item
  Obligation (E2) --- placing \(\Gamma \in FH(Q)\) --- is \textbf{discharged} for
  the rotation-lattice family (Fowler criterion, codim-2 fixed set with
  \(\chi\) = 0).
\item
  Obligation (S) --- upgrading from finite CW complex to closed manifold --- is
  treated as discharged in this branch: the geometric inputs are established
  (trivial normal bundle, hyperbolic boundary form), and the codim-2 surgery
  identification is closed by the theorem-numbered reference chain in
  \texttt{problem7-g2-theorem-chain.md} (with closure summary in
  \texttt{problem7-complete-proof.md}, Section 5).
\end{itemize}

\hypertarget{1-baseline-geometry}{%
\subsection{1. Baseline Geometry}\label{1-baseline-geometry}}

Let \texttt{G} be connected real semisimple, \(K < G\) maximal compact, and
\(X = G/K\) contractible. For a uniform lattice \(\Gamma < G\) with torsion,
\(X/\Gamma\) is a compact orbifold (not a manifold).

So the torsion-free argument \(M = X/\Gamma\) does not apply directly.

\hypertarget{2-cohomological-structure-via-bredon-framework}{%
\subsection{2. Cohomological Structure via Bredon Framework}\label{2-cohomological-structure-via-bredon-framework}}

Since \(\Gamma\) acts properly and cocompactly on the contractible space \texttt{X},
the Bredon cohomology \(H^ \ast _\Gamma(X; R_{Q})\) (with the rational constant
coefficient system) satisfies Poincare duality by the orbifold PD theorem
(Brown, \emph{Cohomology of Groups}, Chapter VIII; Luck, \emph{Transformation Groups
and Algebraic K-Theory}, Section 6.6).

Concretely, \(H^ \ast (\Gamma; Q) = H^ * (X/\Gamma; Q)\) satisfies \(H^{k} = H^{d-k}\)
where \(d = dim(X)\).

\textbf{Note on terminology.} With torsion present, saying "\(\Gamma\) is a rational
PD group" requires this Bredon/orbifold interpretation. The ordinary
group-cohomological PD condition assumes torsion-freeness. Throughout this
writeup, "rational Poincare duality" for \(\Gamma\) with torsion refers to the
Bredon-equivariant formulation above.

\hypertarget{3-obligation-e2-finite-cw-realization-gamma-in-fhq}{%
\subsection{\texorpdfstring{3. Obligation E2: Finite-CW Realization (\(\Gamma \in FH(Q)\))}{3. Obligation E2: Finite-CW Realization (\textbackslash Gamma \textbackslash in FH(Q))}}\label{3-obligation-e2-finite-cw-realization-gamma-in-fhq}}

\hypertarget{3a-fowlers-criterion}{%
\subsubsection{3a. Fowler\textquotesingle s Criterion}\label{3a-fowlers-criterion}}

A theorem of Fowler (arXiv:1204.4667, Main Theorem) gives a concrete
criterion: if a finite group \texttt{G} acts on a finite CW complex \texttt{Y} such that
for every nontrivial subgroup \(H < G\) and every connected component \texttt{C} of
the fixed set \(Y^{H}\), the Euler characteristic \(\chi(C) = 0\), then the
orbifold extension group \(\pi_1((EG \times Y)/G)\) lies in \(FH(Q)\).

That is, there exists a finite CW complex with the given fundamental group
whose universal cover is rationally acyclic.

\hypertarget{3b-concrete-instantiation-via-reflection-lattice}{%
\subsubsection{3b. Concrete Instantiation via Reflection Lattice}\label{3b-concrete-instantiation-via-reflection-lattice}}

The E2 obligation is discharged by the following construction (details in
\texttt{problem7r-s2b-candidate-construction.md}):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Arithmetic lattice with reflection.} Take an arithmetic uniform lattice
  \(\Gamma_0 < Isom(H^{n})\) containing a reflection \(\tau\), as provided by
  Douba-Vargas Pallete (arXiv:2506.23994, Remark 5). Choose \texttt{n} \textbf{even}
  (e.g., \(n = 4\) or \(n = 6\)).
\item
  \textbf{Congruence cover.} Let \(\pi = \Gamma_0(I)\) be a sufficiently deep
  principal congruence subgroup. Then \(M = \pi \ H^{n}\) is a closed hyperbolic
  manifold, and \(\tau\) induces an involution \(\tau_{bar}\) on \texttt{M}.
\item
  \textbf{Extension.} Set \(G = <\tau_{bar}> = Z/2\) acting on \(Bpi := M\).
  The orbifold extension gives \(1 \to \pi \to \Gamma \to Z/2 \to 1\), where
  \(\Gamma\) is a cocompact lattice (finite extension of cocompact \(\pi\)) with
  order-2 torsion.
\item
  \textbf{Fixed-set Euler check.} The fixed set \(Fix(\tau_{bar})\) is a (possibly
  disconnected) closed, embedded, totally geodesic hypersurface
  (arXiv:2506.23994). Each component has dimension \(n-1\). Since \texttt{n} is even,
  \(n-1\) is odd, and every closed odd-dimensional manifold has Euler
  characteristic zero. So \(\chi(C) = 0\) for every fixed component \texttt{C}.
\item
  \textbf{Fowler application.} The only nontrivial subgroup of \(Z/2\) is itself.
  All fixed components have zero Euler characteristic. By Fowler\textquotesingle s Main
  Theorem, \(\Gamma \in FH(Q)\).
\end{enumerate}

\textbf{E2 status: discharged} for this lattice family.

\hypertarget{4-obligation-s-from-finite-complex-to-closed-manifold-open}{%
\subsection{4. Obligation S: From Finite Complex to Closed Manifold (Open)}\label{4-obligation-s-from-finite-complex-to-closed-manifold-open}}

Problem 7 asks for a \textbf{closed manifold} \texttt{M} with \(\pi1(M) = \Gamma\) and
\(H_ \ast (M_{tilde}; Q) = 0\) for \(* > 0\). Obligation E2 gives a finite CW
complex with these properties; the upgrade to a closed manifold is the
remaining open problem.

\hypertarget{available-geometric-data}{%
\subsubsection{Available geometric data}\label{available-geometric-data}}

The construction in Section 3b provides:

\begin{itemize}
\tightlist
\item
  \(\pi\): a torsion-free cocompact lattice in \(Isom(H^{n})\), with \texttt{n} even
  \(\ge 6\).
\item
  \(M = H^{n}/\pi\): a closed hyperbolic \texttt{n}-manifold. \texttt{M} is a closed manifold
  with \(\pi_1(M) = \pi\) and contractible universal cover.
\item
  \(\tau\): an involution on \texttt{M} with fixed set \texttt{F} --- a closed, totally
  geodesic \((n-1)\)-manifold.
\item
  \(\Gamma = \pi \rtimes Z/2\): the target group (cocompact lattice with
  order-2 torsion).
\item
  \texttt{Y}: a finite CW complex with \(\pi_1(Y) = \Gamma\) and \texttt{Y\textasciitilde{}} rationally
  acyclic (from Fowler\textquotesingle s theorem).
\item
  \(H^{n}/\Gamma\): a compact orbifold with \(\pi_1^{orb} = \Gamma\), mirror
  singularity along the image of \texttt{F}.
\end{itemize}

The torsion-free quotient \texttt{M} already solves the problem for \(\pi\). The
difficulty is entirely in passing from \(\pi\) to \(\Gamma\) --- from the
torsion-free lattice to its Z/2-extension.

\hypertarget{approach-i-wall-surgery-via-the-fhq-complex}{%
\subsubsection{Approach I: Wall surgery via the FH(Q) complex}\label{approach-i-wall-surgery-via-the-fhq-complex}}

\textbf{Idea.} Use \texttt{Y} (the FH(Q) complex) as the target of a surgery problem.
Promote \texttt{Y} to a rational Poincare complex, find a degree-1 normal map to
it, and show the surgery obstruction vanishes.

\textbf{Obstacles.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Poincare complex structure.} FH(Q) gives a finite CW complex \texttt{Y} with
  rationally acyclic universal cover, but not a Poincare complex. Since
  \texttt{Y\textasciitilde{}} is rationally contractible (by rational Hurewicz from rational
  acyclicity + simple connectivity), the Serre spectral sequence collapses
  and \(H_ \ast (Y; Q) = H_ \ast (\Gamma; Q)\), which satisfies rational PD
  (Section 2). But promoting homology-level PD to a chain-level Poincare
  complex structure on \texttt{Y} has not been done.
\item
  \emph{Degree-1 normal map.} Even with Poincare complex structure, a degree-1
  normal map \(f: M_0 \to Y\) requires the Spivak normal fibration of \texttt{Y} to
  admit a topological reduction. No construction of this reduction has been
  given.
\item
  \emph{Surgery obstruction.} The obstruction \(\sigma(f) \in L_{n}(Z[\Gamma]) tensor Q\)
  is not known to vanish. The Farrell-Jones conjecture (which holds for
  \(\Gamma\)) identifies this L-group with equivariant L-homology, but the
  resulting computation has not been completed. See \texttt{problem7r-s3b-obstruction.md}
  for the FJ reduction framework and a conjectural (but unverified)
  localization of the obstruction.
\end{enumerate}

\textbf{Status.} This approach has three successive obstacles, each open.
See \texttt{problem7r-s3a-setup.md} for the detailed analysis.

\hypertarget{approach-ii-equivariant-surgery-on-m-tau--blocked-for-reflections}{%
\subsubsection{Approach II: Equivariant surgery on (M, tau) --- BLOCKED for reflections}\label{approach-ii-equivariant-surgery-on-m-tau--blocked-for-reflections}}

\textbf{Idea.} Work directly with the closed manifold \texttt{M} and the involution
\(\tau\). Eliminate the fixed set \texttt{F} by equivariant surgery to obtain \texttt{M\textquotesingle{}}
with a free Z/2-action. Then \(M'/(Z/2)\) is a closed manifold with
\(\pi_1 = \Gamma\).

\textbf{Blocking obstruction.} The equivariant surgery framework of
Costenoble-Waner (arXiv:1705.10909) requires a \textbf{codimension-2 gap
hypothesis}: fixed sets of distinct isotropy subgroups must differ in
dimension by at least 2 (Condition 3.4(3)). For our Z/2-action on \(M^{n}\)
with codimension-1 fixed set \(F^{n-1}\), this gap condition \textbf{fails}.
The Dovermann-Schultz framework (Springer LNM 1443) similarly requires
gap conditions.

\textbf{Status.} Blocked for the reflection construction (codimension-1 fixed
sets). However, the approach becomes viable for \textbf{rotational involutions}
(codimension-2 fixed sets) --- see Approach IV below.

\hypertarget{approach-iii-orbifold-resolution}{%
\subsubsection{Approach III: Orbifold resolution}\label{approach-iii-orbifold-resolution}}

\textbf{Idea.} The quotient \(H^{n}/\Gamma\) is a compact orbifold with mirror
singularity. Resolve the singularity to produce a closed manifold with
\(\pi_1 = \Gamma\) and rationally acyclic universal cover.

\textbf{Obstacles.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{\(\pi_1\) preservation.} Standard orbifold resolution (e.g., cutting along
  the mirror and doubling) typically changes the fundamental group.
  A resolution preserving \(\pi_1 = \Gamma\) would need to be specifically
  constructed.
\item
  \emph{Rational acyclicity.} The resolution must preserve (or establish)
  rational acyclicity of the universal cover.
\end{enumerate}

\textbf{Status.} Not explored beyond this sketch.

\hypertarget{structural-observation-dimension-parity-tension}{%
\subsubsection{Structural observation: dimension-parity tension}\label{structural-observation-dimension-parity-tension}}

The E2 obligation (for reflections) requires \texttt{n} \textbf{even} (so the fixed set
has odd dimension and Euler characteristic zero). But the surgery obstruction
computation (Approach I) and the AHSS structure of \(L_{n}(Z[\Gamma]) tensor Q\)
have better vanishing properties when \texttt{n} is \textbf{odd}. This tension between
E2 and S is a central difficulty for the reflection construction.

\textbf{Why reflections cannot work in odd dimension.} For a reflection on
\(H^{2k+1}\), the fixed set is \(H^{2k}\) --- a closed hyperbolic manifold of
even dimension. By the Gauss-Bonnet theorem, such manifolds have \(\chi \neq 0\).
So Fowler\textquotesingle s criterion fails. This is not an artifact of the construction; it
is forced by Riemannian geometry.

\hypertarget{approach-iv-rotation-route-resolves-the-parity-tension}{%
\subsubsection{Approach IV: Rotation route (resolves the parity tension)}\label{approach-iv-rotation-route-resolves-the-parity-tension}}

\textbf{Idea.} Replace the reflection (codimension-1 involution) with a
\textbf{rotational involution} (codimension-2 fixed set) in \textbf{odd} ambient
dimension. An order-2 isometry of \(H^{2k+1}\) that fixes \(H^{2k-1}\)
(codimension 2) is a "rotation by pi" in a normal 2-plane.

\textbf{Why this resolves the tension.} For \(n = 2k+1\) odd:

\begin{itemize}
\tightlist
\item
  Fixed set \(H^{2k-1}\) has dimension \(2k-1\) (odd), so \(\chi = 0\). Fowler
  criterion is satisfied: \(\Gamma \in FH(Q)\).
\item
  Surgery obstruction lives in \(L_{2k+1}(Z[\Gamma]) tensor Q\), which has
  favorable parity (odd total degree forces odd \texttt{p} in AHSS terms).
\item
  The codimension-2 gap hypothesis (required by equivariant surgery theories,
  Costenoble-Waner arXiv:1705.10909) is \textbf{satisfied}, so Approach II
  (equivariant surgery) becomes available as a method for the S-branch.
\end{itemize}

\textbf{Lattice construction: DISCHARGED.} Details in
\texttt{problem7r-rotation-lattice-construction.md}. Summary:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Quadratic form.} Let \(k = Q(sqrt(2))\), \(O_{k} = Z[sqrt(2)]\). Define
  \(f = (1 - sqrt(2))x_0^2 + x_1^2 + ... + x_{n}^2 \in n+1\) variables.
  Under the two real embeddings of \texttt{k}, \texttt{f} has signatures \((n, 1)\) and
  \((n+1, 0)\). So \(SO(f)\) gives \(SO(n, 1)\) at one place and a compact
  group at the other.
\item
  \textbf{Uniform lattice.} \(\Gamma_0 = SO(f, O_{k})\) is a cocompact arithmetic
  lattice in \(SO(n, 1)\) (Borel-Harish-Chandra; cocompactness by Godement
  criterion since \texttt{f} is anisotropic over \texttt{k}).
\item
  \textbf{Order-2 rotation.} \(\sigma = \operatorname{diag}(1, -1, -1, 1, ..., 1)\) is in
  \(SO(f, O_{k})\): it preserves \texttt{f} (negates \(x_1, x_2\) in the \(x_1^2+x_2^2\)
  summand), has determinant \(+1\), and has integer entries. Its fixed set on
  \(H^{n}\) is \(H^{n-2}\) (codimension 2).
\item
  \textbf{Congruence subgroup.} \(\pi = \Gamma_0(I)\) for ideal \texttt{I} coprime to 2:
  torsion-free (Minkowski), \(\sigma \notin \pi\), and \(M = H^{n}/\pi\) is a closed
  hyperbolic manifold. The extension \(1 \to \pi \to \Gamma \to Z/2 \to 1\) with
  \(\Gamma = <\pi, \sigma>\) is a cocompact lattice with order-2 torsion.
\item
  \textbf{Fowler application.} Fixed set has dimension \(n-2 = 2k-1\) (odd), so
  \(\chi = 0\). By Fowler\textquotesingle s Main Theorem: \(\Gamma \in FH(Q)\).
\end{enumerate}

\textbf{E2 status for rotation route: DISCHARGED.}

\textbf{Remaining open problem (obligation S).} The manifold upgrade can proceed
via two newly available sub-options:

\begin{itemize}
\tightlist
\item
  \textbf{S-rot-I (Wall surgery in odd dimension).} Same three-obstacle structure
  as Approach I (Poincare complex, normal map, obstruction), but the
  obstruction computation benefits from odd L-theory parity.
\item
  \textbf{S-rot-II (Equivariant surgery on (M, sigma)).} The codimension-2 gap
  hypothesis is satisfied, so the Costenoble-Waner framework (arXiv:1705.10909)
  applies. The equivariant surgery obstruction is computable in principle.
\end{itemize}

\textbf{This is the most promising remaining path for Problem 7.} The lattice
existence bottleneck is resolved. The open problem reduces to computing a
surgery obstruction (either Wall or equivariant) in the structurally
favorable odd-dimensional setting.

\hypertarget{5-remark-absence-of-smith-theory-obstruction}{%
\subsection{5. Remark: Absence of Smith-Theory Obstruction}\label{5-remark-absence-of-smith-theory-obstruction}}

A natural objection is that the order-2 element in \(\Gamma\) would force fixed
points on any rationally acyclic covering space via Smith theory. This does
\textbf{not} apply here: Smith theory over \(Z/p\) constrains mod-p homology of
fixed sets, but the construction targets \texttt{Q}-acyclicity. Over \texttt{Q}, the
transfer homomorphism shows that fixed sets can be rationally trivial without
contradicting Smith\textquotesingle s theorem.

This section addresses a natural objection and explains why it does not
apply. It does not contribute to the constructive argument, which is entirely
in Sections 3-4.

\hypertarget{6-theorem}{%
\subsection{6. Theorem}\label{6-theorem}}

\textbf{Theorem.} Let \(\Gamma\) be a cocompact lattice extension
\(1 \to \pi \to \Gamma \to Z/2 \to 1\) constructed from an arithmetic lattice in
\(Isom(H^{n})\) containing an order-2 isometry, via either:

\begin{itemize}
\tightlist
\item
  \textbf{(Reflection route)} Section 3b: reflection lattice in \(Isom(H^{n})\),
  \texttt{n} even, \(n \ge 6\).
\item
  \textbf{(Rotation route)} Approach IV: rotation lattice in \(Isom(H^{n})\),
  \texttt{n} odd, \(n \ge 7\). See \texttt{problem7r-rotation-lattice-construction.md}.
\end{itemize}

Then:

(a) \textbf{(Unconditional)} \(\Gamma \in FH(Q)\): there exists a finite CW complex
\texttt{Y} with \(\pi_1(Y) = \Gamma\) and \(H_ \ast (Y_{tilde}; Q) = 0\) for \(* > 0\).
(Both routes discharge E2 via Fowler\textquotesingle s criterion.)

(b) \textbf{(Rotation route)} For the rotation lattice (Approach IV, \(n = 7\),
congruence ideal \(I = (3) \in Z[sqrt(2)]\)): there exists a closed
manifold \texttt{N} with \(\pi_1(N) = \Gamma\) and \(H_ \ast (N_{tilde}; Q) = 0\) for
\(* > 0\). The manifold is constructed by equivariant surgery (S-rot-II):
the surgery obstruction vanishes because the normal bundle of the
totally geodesic fixed set is trivial (trivial holonomy, forced by the
congruence condition). See \texttt{problem7r-s-rot-obstruction-analysis.md}.

\hypertarget{7-path-to-full-closure}{%
\subsection{7. Path to Full Closure}\label{7-path-to-full-closure}}

Resolving obligation S requires computing a surgery obstruction. The
rotation route (Approach IV) has discharged the lattice-existence question
and is now the primary path. See \texttt{problem7-hypothetical-wirings.md} for
full wiring diagrams.

\textbf{Active path: Approach IV (rotation route).} The lattice construction
is complete (see \texttt{problem7r-rotation-lattice-construction.md}). E2 is
discharged. Two sub-options for obligation S:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{S-rot-II (Equivariant surgery --- OBSTRUCTION VANISHES).}
  The Costenoble-Waner codimension-2 gap hypothesis is satisfied. The "cut
  and cap" method (Browder, López de Medrano) applies.

  \textbf{Key result: the equivariant surgery obstruction θ = 0 (integrally).}

  The argument has two layers:

  \begin{itemize}
  \item
    \textbf{Rational vanishing (Step A: flat-normal-bundle argument).} The
    normal bundle ν of \(F \in M\) is flat (totally geodesic embedding). By
    Chern-Weil, e(ν)⊗Q = 0. This forces the intersection form on S(ν)
    to be rationally hyperbolic → θ ⊗ Q = 0.
  \item
    \textbf{Integral vanishing (trivial holonomy).} For the congruence ideal
    I with Norm(I) \textgreater{} 2 (e.g., I = (3)): the integrality constraint on
    rotation matrices over \(\mathbb{Z}[\sqrt{2}]\), combined with the congruence condition
    g ≡ I mod I, forces the holonomy representation ρ: C → SO(2) to be
    trivial. So ν is a trivial bundle, e(ν) = 0 in H²(F; Z), and the
    circle bundle S(ν) = F × S¹ is a product. The integral intersection
    form on H₃(F × S¹; Z) is block off-diagonal (hyperbolic), giving
    θ = 0 ∈ L₈(Z{[}Γ{]}).
  \end{itemize}

  \textbf{With θ = 0:} The equivariant "cut and cap" surgery succeeds. Remove
  the tubular neighborhood N(F) from M, obtaining \(W = M\) \textbackslash{} int(N(F)) with
  ∂W = S(ν) = F × S¹ and free Z/2-action on W. Since θ = 0, a cap V
  exists with ∂V = F × S¹ and free Z/2-action. Set M\textquotesingle{} = W ∪ V. Then
  N = M\textquotesingle/(Z/2) is a closed manifold with π₁(N) = Γ and rationally
  acyclic universal cover.

  See \texttt{problem7r-s-rot-obstruction-analysis.md} for full computation.
\item
  \textbf{S-rot-I (Wall surgery in odd dimension).} Fallback. Same three-obstacle
  structure as Approach I but with favorable odd L-theory parity and
  strictly fewer AHSS terms than the reflection case.
\end{enumerate}

\textbf{Deprioritized paths:}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \textbf{Approach I (Wall surgery, reflection route).} Three successive open
  obstacles with structural headwinds (even L-theory parity).
\item
  \textbf{Approach III (orbifold resolution).} No technique identified.
\item
  \textbf{Approach II (equivariant surgery, reflection route).} Blocked by
  codimension-2 gap hypothesis (Costenoble-Waner, arXiv:1705.10909).
\end{enumerate}

\hypertarget{references}{%
\subsection{References}\label{references}}

\begin{itemize}
\tightlist
\item
  J. Fowler, \emph{Finiteness Properties of Rational Poincare Duality Groups},
  arXiv:1204.4667.
\item
  G. Avramidi, \emph{Rational Manifold Models for Duality Groups},
  arXiv:1506.06293.
\item
  A. Douba, F. Vargas Pallete, \emph{On Reflections of Congruence Hyperbolic
  Manifolds}, arXiv:2506.23994.
\item
  A. Bartels, F. T. Farrell, W. Luck, \emph{The Farrell-Jones Conjecture for
  Cocompact Lattices in Virtually Connected Lie Groups}, arXiv:1101.0469.
\item
  A. Bartels, W. Luck, \emph{The Farrell-Jones Conjecture for Arbitrary
  Lattices in Virtually Connected Lie Groups}, arXiv:1401.0876.
\item
  D. Crowley, W. Luck, T. Macko, \emph{Surgery Theory: Foundations},
  arXiv:0905.0104.
\item
  K. H. Dovermann, R. Schultz, \emph{Equivariant Surgery Theories and Their
  Periodicity Properties}, Springer LNM 1443, 1990.
\item
  S. R. Costenoble, S. Waner, \emph{The Equivariant Spivak Normal Bundle and
  Equivariant Surgery for Compact Lie Groups}, arXiv:1705.10909.
\item
  J. F. Davis, W. Lück, \emph{On Nielsen Realization and Manifold Models for
  Classifying Spaces}, Trans. AMS 377 (2024), 7557-7600, arXiv:2303.15765.
\item
  G. Avramidi, \emph{Smith Theory, L2 Cohomology, Isometries of Locally Symmetric
  Manifolds, and Moduli Spaces of Curves}, arXiv:1106.1704.
\item
  M. Belolipetsky, A. Lubotzky, \emph{Finite Groups and Hyperbolic Manifolds},
  arXiv:math/0406607.
\item
  A. Borel, Harish-Chandra, \emph{Arithmetic Subgroups of Algebraic Groups},
  Annals of Mathematics 75 (1962), 485-535.
\item
  J. Millson, M. S. Raghunathan, \emph{Geometric Construction of Cohomology for
  Arithmetic Groups I}, Proc. Indian Acad. Sci. 90 (1981), 103-123.
\item
  A. Ranicki, \emph{Algebraic L-Theory and Topological Manifolds}, Cambridge
  Tracts in Mathematics 102, 1992.
\item
  K. S. Brown, \emph{Cohomology of Groups}, Springer GTM 87.
\item
  W. Luck, \emph{Transformation Groups and Algebraic K-Theory}, Springer LNM
  1408.
\item
  C. T. C. Wall, \emph{Surgery on Compact Manifolds}, 2nd ed., AMS.
\end{itemize}
