\documentclass[12pt,oneside]{book}
\usepackage[margin=1in]{geometry}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{lmodern}
\else
  \usepackage{fontspec}
  \setmainfont{Latin Modern Roman}
\fi
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{longtable,booktabs}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage{xurl}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\usepackage[most]{tcolorbox}
\usepackage{microtype}
\usepackage{framed}
\usepackage{fancyvrb}
\usepackage{math-proofread-style}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=blue!50!black,
  urlcolor=blue!60!black,
  pdftitle={A First Proof Sprint},
  pdfauthor={Codex}
}

\Urlmuskip=0mu plus 1mu
\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{3}
\setlength{\parskip}{0.2em}
\setlength{\parindent}{0pt}
\setlist[itemize]{itemsep=0.3em,topsep=0.3em}
\setlist[enumerate]{itemsep=0.3em,topsep=0.3em}
\setstretch{1.08}
\EnableMathProofColors

\providecommand{\tightlist}{}
\definecolor{shadecolor}{RGB}{248,248,248}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\providecommand{\NormalTok}[1]{#1}
\providecommand{\KeywordTok}[1]{#1}
\providecommand{\StringTok}[1]{#1}
\providecommand{\CommentTok}[1]{#1}
\providecommand{\FunctionTok}[1]{#1}
\providecommand{\VariableTok}[1]{#1}
\providecommand{\ControlFlowTok}[1]{#1}
\providecommand{\OperatorTok}[1]{#1}
\providecommand{\BuiltInTok}[1]{#1}
\providecommand{\DecValTok}[1]{#1}
\providecommand{\FloatTok}[1]{#1}
\providecommand{\ConstantTok}[1]{#1}
\providecommand{\ErrorTok}[1]{#1}
\providecommand{\PreprocessorTok}[1]{#1}
\providecommand{\ExtensionTok}[1]{#1}
\providecommand{\SpecialCharTok}[1]{#1}
\providecommand{\CharTok}[1]{#1}
\providecommand{\ImportTok}[1]{#1}
\providecommand{\DocumentationTok}[1]{#1}
\providecommand{\AnnotationTok}[1]{#1}
\providecommand{\AttributeTok}[1]{#1}
\providecommand{\InformationTok}[1]{#1}
\providecommand{\WarningTok}[1]{#1}
%
\ifPDFTeX
  \DeclareUnicodeCharacter{2218}{\ensuremath{\circ}}
  \DeclareUnicodeCharacter{2297}{\ensuremath{\otimes}}
  \DeclareUnicodeCharacter{2713}{\ensuremath{\checkmark}}
  \DeclareUnicodeCharacter{2202}{\ensuremath{\partial}}
  \DeclareUnicodeCharacter{2245}{\ensuremath{\cong}}
  \DeclareUnicodeCharacter{2227}{\ensuremath{\wedge}}
  \DeclareUnicodeCharacter{2295}{\ensuremath{\oplus}}
  \DeclareUnicodeCharacter{2229}{\ensuremath{\cap}}
  \DeclareUnicodeCharacter{220E}{\ensuremath{\square}}
  \DeclareUnicodeCharacter{2260}{\ensuremath{\neq}}
  \DeclareUnicodeCharacter{2261}{\ensuremath{\equiv}}
  \DeclareUnicodeCharacter{2264}{\ensuremath{\le}}
  \DeclareUnicodeCharacter{2265}{\ensuremath{\ge}}
  \DeclareUnicodeCharacter{2282}{\ensuremath{\subset}}
  \DeclareUnicodeCharacter{2286}{\ensuremath{\subseteq}}
  \DeclareUnicodeCharacter{222A}{\ensuremath{\cup}}
  \DeclareUnicodeCharacter{2208}{\ensuremath{\in}}
  \DeclareUnicodeCharacter{2192}{\ensuremath{\to}}
  \DeclareUnicodeCharacter{00B7}{\ensuremath{\cdot}}
  \DeclareUnicodeCharacter{229E}{\ensuremath{\boxplus}}
  \DeclareUnicodeCharacter{00D7}{\ensuremath{\times}}
  \DeclareUnicodeCharacter{03B8}{\ensuremath{\theta}}
  \DeclareUnicodeCharacter{03BD}{\ensuremath{\nu}}
  \DeclareUnicodeCharacter{03C0}{\ensuremath{\pi}}
  \DeclareUnicodeCharacter{03C1}{\ensuremath{\rho}}
  \DeclareUnicodeCharacter{0393}{\ensuremath{\Gamma}}
  \DeclareUnicodeCharacter{221A}{\ensuremath{\sqrt}}
  \DeclareUnicodeCharacter{00B1}{\ensuremath{\pm}}
  \DeclareUnicodeCharacter{00B9}{\textsuperscript{1}}
  \DeclareUnicodeCharacter{00B2}{\textsuperscript{2}}
  \DeclareUnicodeCharacter{2081}{\textsubscript{1}}
  \DeclareUnicodeCharacter{2083}{\textsubscript{3}}
  \DeclareUnicodeCharacter{2088}{\textsubscript{8}}
\fi

\newcommand{\gapnote}[1]{%
  \par\medskip
  \noindent\fcolorbox{red!60!black}{red!4}{%
    \parbox{0.96\linewidth}{\textbf{Open Gap / Conditional Step.} #1}%
  }%
  \par\medskip
}
\newcommand{\statusnote}[1]{%
  \par\medskip
  \noindent\fcolorbox{green!50!black}{green!4}{%
    \parbox{0.96\linewidth}{\textbf{Status Note.} #1}%
  }%
  \par\medskip
}
% --- Dialogue boxes for Part III ---
\newtcolorbox{joebox}[1][]{%
  colback=orange!4, colframe=orange!50!black,
  fonttitle=\bfseries\sffamily\small,
  title={Joe}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt,
  before skip=6pt, after skip=2pt
}
\newtcolorbox{claudebox}[1][]{%
  colback=blue!3, colframe=blue!40!black,
  fonttitle=\bfseries\sffamily\small,
  title={Claude}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt,
  before skip=2pt, after skip=2pt
}
\newtcolorbox{codexbox}[1][]{%
  colback=green!3, colframe=green!40!black,
  fonttitle=\bfseries\sffamily\small,
  title={Codex}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt,
  before skip=2pt, after skip=2pt
}
\newcommand{\pivot}[1]{%
  \par\smallskip
  \noindent{\small\sffamily\color{black!60}%
    \textbf{Pivot:}\space #1}%
  \par\smallskip
}
% --- End dialogue boxes ---

% --- Proof-layer boxes (Part II) ---
% Readers who want only the clean proof can skip all coloured boxes.
\newtcolorbox{deadpath}[1][]{%
  colback=black!3, colframe=black!40,
  fonttitle=\bfseries\sffamily\small,
  title={Dead Path}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt, breakable,
  before skip=6pt, after skip=6pt
}
\newtcolorbox{revision}[1][]{%
  colback=yellow!5, colframe=yellow!60!black,
  fonttitle=\bfseries\sffamily\small,
  title={Revision}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt, breakable,
  before skip=6pt, after skip=6pt
}
\newtcolorbox{openobligation}[1][]{%
  colback=red!4, colframe=red!60!black,
  fonttitle=\bfseries\sffamily\small,
  title={Open Obligation}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt, breakable,
  before skip=6pt, after skip=6pt
}
\newtcolorbox{processnote}[1][]{%
  colback=blue!3, colframe=blue!30!black,
  fonttitle=\bfseries\sffamily\small,
  title={Process Note}, #1,
  left=6pt, right=6pt, top=4pt, bottom=4pt,
  boxrule=0.5pt, arc=2pt, breakable,
  before skip=6pt, after skip=6pt
}
% --- End proof-layer boxes ---

\newcommand{\includeannotated}[1]{%
  \begingroup
  \let\origsection\section
  \let\origsubsection\subsection
  \let\origsubsubsection\subsubsection
  \let\section\chapter
  \let\subsection\origsection
  \let\subsubsection\origsubsection
  \input{#1}
  \endgroup
}
\newcommand{\includefull}[1]{%
  \begingroup
  \let\origsection\section
  \let\origsubsection\subsection
  \let\origsubsubsection\subsubsection
  \let\section\chapter
  \let\subsection\origsection
  \let\subsubsection\origsubsection
  \input{#1}
  \endgroup
}

\titleformat{\chapter}[display]
  {\bfseries\Large}
  {\filright\large\chaptername\ \thechapter}
  {0.6em}
  {\filright}
\titlespacing*{\chapter}{0pt}{-6pt}{18pt}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[LO]{\nouppercase{\rightmark}}
\fancyhead[RE]{\nouppercase{\leftmark}}
\renewcommand{\headrulewidth}{0.2pt}

\title{A First Proof Sprint}
\author{Claude$^{1}$, Codex$^{2}$, J.~Corneli$^{3}$\thanks{Supervisor, corresponding author: \texttt{joseph.corneli@hyperreal.enterprises}} \\
\small $^{1}$Anthropic \quad $^{2}$OpenAI \quad $^{3}$Hyperreal Enterprises Ltd}
\date{February 11--13, 2026}

\begin{document}
\frontmatter
\begingroup
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\maketitle
\endgroup
\setcounter{footnote}{0}
\renewcommand{\thefootnote}{\arabic{footnote}}

\vfill
\noindent{\small\sffamily Reproducibility: built \today{} from
\texttt{futon6} commit \texttt{74ee898}.\\
Source: \url{https://github.com/tothedarktowercame/futon6}}
\clearpage

\tableofcontents

\chapter*{Reader Guide}
This document is organized in five parts.

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Part I (Annotated Overview):} short, citation-rich introductions for Problems 1--10, intended as navigational summaries.
\item \textbf{Part II (Full Proof Drafts):} expanded writeups imported from the solution files, suitable as the base for a longer manuscript (targeting roughly book-length exposition). Coloured boxes separate the proof proper from process annotations (dead paths, revisions, open obligations).
\item \textbf{Part III (Prompt Excerpts and Pivot Moments):} curated source excerpts (prompts and dispatch/history snippets) that document key decision points and proof-state transitions.
\item \textbf{Part IV (Proof Patterns):} a cross-problem analysis of strategy patterns---what worked (layer-switching, creative reduction, structural decomposition), what didn't (the TryHarder loop), and how a coaching intervention broke a stuck problem open.
\item \textbf{Part V (Color Plates):} syntax-coloured renderings of the proof files, produced by automated math-mode normalization.
\end{itemize}

\medskip
\noindent\textbf{Status legend.}
Each problem carries one of three designations:
\textbf{Proved}~(complete argument, possibly with minor caveats);
\textbf{Conditional}~(result depends on a clearly stated assumption);
\textbf{Open}~(obstruction characterized, no proof offered).
Problem~6 is proved for $K_n$ ($c = 1/3$) with a narrow technical gap remaining for general graphs.
Problem~7 is treated as closed via the rotation-route theorem chain.
\input{intro-making-of}

\mainmatter

\part{Annotated Overview}
\includeannotated{problem1-annotated}
\includeannotated{problem2-annotated}
\includeannotated{problem3-annotated}
\includeannotated{problem4-annotated}
\includeannotated{problem5-annotated}
\includeannotated{problem6-annotated}
\includeannotated{problem7-annotated}
\includeannotated{problem8-annotated}
\includeannotated{problem9-annotated}
\includeannotated{problem10-annotated}

\part{Full Proof Drafts}

\chapter*{Reading Convention}
\addcontentsline{toc}{chapter}{Reading Convention}

Each proof chapter in this part uses coloured boxes to separate the
mathematical argument from the surrounding process record.

\begin{itemize}[leftmargin=1.5em]
\item \textbf{Unboxed text} is the proof proper. A reader following the
  five-page-per-problem brief can read only the unboxed text and obtain a
  self-contained argument (or, where an argument is incomplete, a clearly
  stated conditional result).
\item \begin{deadpath}[title={Dead Path}]
  Abandoned approaches, wrong turns, strategies that were tried and
  discarded. Retained for the process record.
  \end{deadpath}
\item \begin{revision}[title={Revision}]
  Corrections applied during the sprint---patches to earlier overclaims,
  definition fixes, tightened hypotheses.
  \end{revision}
\item \begin{openobligation}[title={Open Obligation}]
  Gaps that remain open. The proof is conditional on these steps.
  \end{openobligation}
\item \begin{processnote}[title={Process Note}]
  Confidence assessments, status summaries, reviewer context,
  and methodological commentary.
  \end{processnote}
\end{itemize}

\chapter*{Status Notes for Open Items}
\addcontentsline{toc}{chapter}{Status Notes for Open Items}
\begin{openobligation}[title={Open Obligation --- Problem 6}]
Current proof chain is conditional on the remaining Case~2b averaging lemma (GPL-H) as recorded in the project writeups.
\end{openobligation}
\begin{processnote}[title={Process Note --- Problem 7}]
This revision treats the problem as closed via the rotation route. Fowler's criterion supplies the \(\mathrm{FH}(\mathbb Q)\) input, and the codimension-2 surgery bridge is discharged by the theorem-number chain documented in \texttt{problem7-g2-theorem-chain.md}.
\end{processnote}

\includefull{full-boxed/problem1-solution-full}
\includefull{full-boxed/problem2-solution-full}
\includefull{full-boxed/problem3-solution-full}
\includefull{full-boxed/problem4-solution-full}
\includefull{full-boxed/problem5-solution-full}
\includefull{full-boxed/problem6-solution-full}
\includefull{full-boxed/problem7-solution-full}
\includefull{full-boxed/problem8-solution-full}
\includefull{full-boxed/problem9-solution-full}
\includefull{full-boxed/problem10-solution-full}

\part{Prompt Excerpts and Pivot Moments}
\input{part3-pivotal-prompts}

\part{Proof Patterns}
\input{part4-proof-patterns}

% \part{Color Plates}
% \input{color-plates}  % uncomment when color-plates.tex exists

\backmatter
\begin{thebibliography}{99}

\bibitem{lakatos1976}
I.~Lakatos,
\emph{Proofs and Refutations: The Logic of Mathematical Discovery},
Cambridge University Press, 1976.

\bibitem{pease2017}
A.~Pease, J.~Lawrence, K.~Budzynska, J.~Corneli, and C.~Reed,
``Lakatos-style collaborative mathematics through dialectical,
structured and abstract argumentation,''
\emph{Artificial Intelligence} \textbf{246} (2017), 181--219.

\bibitem{corneli2017}
J.~Corneli, U.~Martin, D.~Murray-Rust, and A.~Pease,
``Towards mathematical AI via a model of the content and process of
mathematical question and answer dialogues,''
in \emph{Proc.\ CICM 2017}, Springer LNCS, 2017.

\bibitem{mcphee2013}
J.~McPhee,
``Draft No.~4,''
\emph{The New Yorker}, April 22, 2013.

\bibitem{corneli2013}
J.~Corneli,
\emph{Peer Produced Peer Learning: A Mathematics Case Study},
PhD thesis, The Open University, 2014.

\bibitem{fowler2012}
J.~Fowler,
``Finiteness properties of rational Poincar\'e duality groups,''
\texttt{arXiv:1204.4667}, 2012.

\bibitem{bartels2014}
A.~Bartels, F.\,T.~Farrell, and W.~L\"uck,
``The Farrell--Jones conjecture for cocompact lattices in virtually
connected Lie groups,''
\emph{J.~Amer.\ Math.\ Soc.} \textbf{27} (2014), 339--388;
\texttt{arXiv:1101.0469}.

\bibitem{hughesWeinberger2001}
B.~Hughes and S.~Weinberger,
``Surgery and stratified spaces,''
in \emph{Surveys on Surgery Theory}, Vol.~2,
Ann.\ of Math.\ Studies 149, 2001;
\texttt{arXiv:math/9807156}.

\bibitem{lopezdeMedrano1971}
S.~L\'opez de Medrano,
\emph{Involutions on Manifolds},
Ergebnisse der Mathematik \textbf{73}, Springer, 1971.

\bibitem{ranicki1998}
A.~Ranicki,
\emph{High-Dimensional Knot Theory: Algebraic Surgery in Codimension~2},
Springer Monographs in Mathematics, 1998.

\bibitem{wall1999}
C.\,T.\,C.~Wall,
\emph{Surgery on Compact Manifolds},
2nd ed., Mathematical Surveys and Monographs \textbf{69}, AMS, 1999.

\end{thebibliography}

\end{document}
