\chapter*{Part III: The Sprint as Dialogue}
\addcontentsline{toc}{chapter}{Part III: The Sprint as Dialogue}

This chapter records the proof sprint as it actually happened: a
conversation between a human dispatcher (Joe), two AI proof engines
(Claude instances), and a verifier/researcher (Codex), conducted over
roughly 48 hours on February 11--13, 2026. Excerpts are drawn from
\texttt{history.jsonl} (Joe's prompts), Codex output files, and git
commit messages. Editorial annotations mark the pivotal moments where
proof strategy, status, or architecture shifted.

\bigskip

%% ============================================================
\section*{Act I: ``Even if we're a day late''}
%% ============================================================

\begin{joebox}
Claude + Joe Solve ``First Proof'' using Rob's Superpod
\url{https://arxiv.org/html/2602.05192v1}
\end{joebox}

\begin{joebox}
Even if we're a day late and a dollar short at least we can try
\end{joebox}

\begin{joebox}
Let's see if we can do one of them right now using PlanetMath and nlab
and off-the-shelf Claude
\end{joebox}

\pivot{The sprint begins. Problem~10 is chosen as a warm-up.
  Within 30~minutes it is solved, and the pace accelerates.}

\begin{joebox}
OK, should we solve another First Proof problem? The last one wasn't
so hard apparently!
\end{joebox}

%% ============================================================
\section*{Act II: Scaling the Machinery}
%% ============================================================

\begin{joebox}
OK, I have two Codex research assistants working for you as well as
the validator working on p6
\end{joebox}

\begin{joebox}
OK, we have 3~verifiers running now, they are making progress but not
committing yet
\end{joebox}

\begin{joebox}
Codex is \emph{still} after 53~minutes hard at work on Problem~6, but
it is down to two gaps now. I think 3~verifiers is about all my
laptop can handle, noticing considerable slow down.
\end{joebox}

\begin{joebox}
I think I will give it five more minutes and then say ``pencils down''
and let you look at \#6
\end{joebox}

\begin{joebox}
Codex is pushing \#6, I OOMed on 3 and 5, I will get them back up
once 6~lands
\end{joebox}

\pivot{Physical resource limits (RAM, thermal throttling) become a
  genuine constraint on mathematical exploration. The multi-agent
  topology stabilises at three concurrent processes.}

\begin{joebox}
It's slow going over here---are any of the proofs sufficiently
validated that we could start a ``write up''? If the previous
example is representative it can take about an hour for one of
these to complete.
\end{joebox}

%% ============================================================
\section*{Act III: Proofs and Refutations}
%% ============================================================

\begin{joebox}
I have engaged Codex and another Claude in a reviewer +
response-to-reviewer cycle. Codex found some pretty significant
problems; the other Claude is making what look like solid fixes, but
it looks like tough going.
\end{joebox}

\begin{codexbox}[title={Codex --- Triage verdict}]
P8: most recoverable. [\ldots]
P2: recoverable but harder. Needs one serious
representation-theoretic theorem/lemma that is currently hand-waved.
[\ldots]
P7: least recoverable as currently framed. The obstruction-vanishing
step is the main risk; unless they replace it with a precise known
theorem tailored to this lattice family, this will likely remain
conditional/existential rather than a full proof.
\end{codexbox}

\pivot{Codex's triage creates a severity ordering across problems,
  distinguishing ``recoverable'' from ``structural'' gaps.
  The review cycle is now explicitly adversarial: prover vs.\ critic.}

\begin{joebox}
This is interesting in comparison to my work in futon5 on
Meta-Meta-Cellular Automata. There also, generation is cheap---just
bit flipping---but doing things like ``detecting edge of chaos
behaviour'' is a challenge. [\ldots]
However, I think we really haven't done so bad.
We have our Claude-Codex ``Proofs and Refutations'' system up and
running right now, we use both collaborative (verification + library
research) and argumentative (prover vs critic) modes. So
notwithstanding the mathematical issues you raised---at least we
aren't shipping failed proofs! This is verification happening at a
``glacial'' scale in futon3c terminology---but at least it is
happening!
\end{joebox}

\begin{joebox}
Furthermore, the wiring diagram decomposition is probably the only
thing holding this together---it's allowing us to be very targeted
with our reviews and fixes. Imagine trying to do what we're doing
with\ldots\ ChatGPT. It would be hell.
\end{joebox}

\begin{joebox}
Also, another remark---making mistakes isn't a bad thing.
As my grandfather said, that's how we learn.
\end{joebox}

\pivot{A methodological self-assessment. The two key claims:
  (1)~the wiring-diagram decomposition enables targeted review at
  scale; (2)~the collaborative/adversarial agent modes prevent
  ``shipping failed proofs.'' Both claims are tested in
  Acts~IV--V.}

%% ============================================================
\section*{Act IV: Formalization and Futon Theory}
%% ============================================================

\begin{joebox}
This does suggest a possible but probably crazy and stupid idea---which
hasn't stopped hundreds of people trying it. What about formalizing as
we go? Like QED style. I mean, it hurts me to say this. I briefly
had Bob Boyer as a Master's advisor. He and I could not see eye to
eye. Granted, that was 2002 and things were a little different back
then.
\end{joebox}

\begin{joebox}
Yeah, I mean, we needed in 2002 \emph{what we are doing now}. The
only problem is it wasn't possible then.
\end{joebox}

\begin{claudebox}
So in a sense, the 2002 vision was twenty-four years early rather
than wrong.
\end{claudebox}

\begin{joebox}
Better than twenty-four years late! Imagine if I proposed WIFI now.
Great idea right?
\end{joebox}

\pivot{A historical aside connecting the sprint to the 2002-era
  theorem-proving community. The implication: AI-assisted informal
  proof is the approach that was missing, not formalization per~se.}

\begin{joebox}
OK, so the naive idea: could we write a letter to Codex talking about
why Problem~4 is hard? It would use the John McPhee idea~\cite{mcphee2013}\ldots
\end{joebox}

\begin{joebox}
OK, now a non-naive idea (which may be less useful than the naive one).
I invented something called ``futon theory''---it's not quite what it
sounds like. Futons (in my theory) are atoms of the future which are
perceivable in the present. [\ldots]
It's a bit different in mathematics because in principle we don't know
if the result is actually true. But what we could do is design the
search process, and then we would at least know that the search
process is working the way we hoped it would. It's the somewhat more
technical version of the ``Dear Codex'' letter you just
wrote---building a process that you have utter confidence in that
will shed light on the domain even if it doesn't reveal the exact
answer.
\end{joebox}

\pivot{Two ideas collide: McPhee's ``letter to yourself'' technique
  for writer's block, and futon theory's ``atoms of the future.''
  Both converge on the same insight: process design is tractable even
  when the mathematical outcome is uncertain.}

\begin{joebox}
Great, I think you have your work cut out for you. It's cool that
this involved all the strategies, including the ``least likely''
Strategy~C that surprised us by being particularly flavourful
\end{joebox}

%% ============================================================
\section*{Act V: Crisis --- P6 and P7}
%% ============================================================

\begin{joebox}
I thought \#6 and \#7 were proved so I'm glad I asked!
\end{joebox}

\begin{joebox}
Well I am a bit perplexed b/c at this time yesterday I had been
convinced that Problem~7 was done. Look at Problem~7 related git
logs to try and figure out what's been going on with this journey.
\end{joebox}

\begin{joebox}
Well, I have another Codex program mining Arxiv right now for wiring
diagrams that we might use. But this presupposes that we are actually
looking at gaps and not a decomposing corpse.
\end{joebox}

\pivot{The most dramatic moment in the sprint. A problem believed
  closed reopens with structural gaps. The ``decomposing corpse''
  quip captures the uncertainty: is the proof salvageable, or
  fundamentally dead?}

\begin{joebox}
Hm, claim~1 sounds a bit like replacing an overclaim with weasel
words; \#2~similarly. I think we need to restructure the proof?
\end{joebox}

\begin{claudebox}[title={Claude --- Gap triage}]
G1 (fundamental group control) and G3 (rational acyclicity) can be
closed once the cap is homotopy equivalent to $F \times D^2$
rel~boundary. [\ldots] G2 (Browder--Quinn identification) remains
the genuine remaining gap.
\end{claudebox}

\pivot{The monolithic ``open Problem~7'' label is decomposed into a
  prioritised closure queue: G1, G2, G3. Within hours, G1 and G3
  are resolved, isolating G2 as the sole remaining obligation.}

\begin{joebox}
Could we cite secondary literature for G2 that is on Arxiv?
Mathematics is full of folklore
\end{joebox}

\begin{claudebox}[title={Claude --- Citation search result}]
There is no single modern arXiv theorem that states the exact
identification in one line. The bridge is assembled from standard
components: Browder~(1968), L\'opez de Medrano~(1971),
Cappell--Shaneson~(1974), Ranicki~(1998).
\end{claudebox}

\pivot{Citation strategy stabilises: replace ``single theorem lookup''
  with a theorem-number ledger across four classical sources.}

\begin{joebox}
It really sounds to me like the proof of Problem~6 is hanging by a
thread
\end{joebox}

%% ============================================================
\section*{Act VI: Student Dispatch and Agent Teaming}
%% ============================================================

\begin{joebox}
Yeah, I guess the model is rather than treating Codex as a junior
developer as we sometimes do in coding applications, we would treat
them as a ``grad student.''
\end{joebox}

\begin{joebox}
Maybe we should call it student-dispatch to include undergrads, bright
high schoolers, and precocious five year olds like Codex
\end{joebox}

\pivot{The \texttt{agent/student-dispatch} pattern is named. It
  reframes the Codex interaction from ``run this script'' to
  ``here is context, dead ends, directions---explore and report.''}

\begin{joebox}
So I wonder what we could do to help. I've almost run out of ideas.
I guess one pattern I've noticed is that we can support the
``reduction'' pattern by verifying everything that is claimed except
the gap. Closing gaps (as with Problem~4) can sometimes turn out to
be a focused computational task. Another approach is Math Overflow
search or Arxiv search to create wiring diagrams that might help or
might provide analogous reasoning structures. That last part is a bit
woolly.
\end{joebox}

\begin{joebox}
So, if we were able to turn SE into wiring diagrams on the superpod,
then we could use tensor math to search them!
\end{joebox}

\begin{joebox}
Ah, and for ``artificial stack exchange'' what we could do is
\emph{induce} new wiring diagrams, notice where they sit relative to
other known diagrams (this corresponds to ``asking a question'')
\end{joebox}

\pivot{A forward-looking connection: the proof sprint's
  wiring-diagram methodology could be mechanised via tensor search
  over StackExchange-derived argument structures. This motivates
  the Stage~7 thread-wiring work in the futon6 pipeline.}

%% ============================================================
\section*{Act VII: The Coaching Breakthrough (Problem 6)}
%% ============================================================

\begin{joebox}
Well, and I want to talk with you about Problem~6. I think that's the
only one outstanding. But I'm realizing that the ``other Claude'' has
been sending me on continual gap-filling missions without giving me
a valid confidence signal. It's like Gemini saying ``I'll fix your
code right away sir!'' [\ldots] Problem~6 has not brought out the best
in Claude.
\end{joebox}

\begin{joebox}
I think a good approach might be: ``Can you find any other
reductions?'' That would start to build some intelligence around the
pattern rather than just a TryHarder strategy.
\end{joebox}

\pivot{The failure mode is diagnosed: dispatching closure attempts
  without layer-level calibration. The ``reductions'' framing shifts
  from ``close the gap'' to ``map the landscape.''}

\begin{joebox}
I think you should think out of the box a bit. What kind of problem is
this? What kind of proof applies to this kind of problem? How would
you teach it to an undergraduate? How would you teach it to a grad
student? Where, in reality, do people learn about this kind of
problem? What kind of person finds this kind of problem easy? Are
there ``tricks'' (symmetries) that would make some of your Zeno's
Paradoxes go away? Like one from my thesis in the resources directory
is an example from Gowers in which binomial expansion terms have
opposite signs and so cancel. Like, OK, this problem was an ``open
problem'' not a textbook problem but come on---it's on the research
frontier, we're not asking you to solve alien mathematics from the
year~5000AD. This is totally within your capability space. Why aren't
you finding the answer in 30~minutes?
\end{joebox}

\pivot{The coaching intervention. Five questions, each forcing a
  different reframing: layer enumeration (``what kind of problem?''),
  pedagogical reduction (``teach it to an undergrad''), sociological
  targeting (``who finds this easy?''), structural cancellation
  (``tricks / symmetries''), and honest calibration (``why not
  30~minutes?'').}

\begin{claudebox}[title={Claude --- 15 minutes later}]
The proof for $K_n$ is complete. $\bar{d} = 2t/(n\varepsilon) \le 2/3$
at $T = \varepsilon n/3$ steps. Pigeonhole gives $\exists v$ with
$\operatorname{tr}(Y) \le 2/3$, and $\|Y\| \le \operatorname{tr}(Y)$
for PSD matrices. The barrier is maintained at every step.
Result: $|S| = \varepsilon n/3$, $c = 1/3$.
\end{claudebox}

\begin{claudebox}[title={Claude --- The irony}]
The irony: this entire proof is elementary---no interlacing families,
no Borcea--Br\"and\'en, no MSS theorem needed. Just PSD trace bound
$+$ pigeonhole $+$ Tur\'an.

\smallskip
\noindent\emph{[With the benefit of hindsight: the elementary proof
closes $K_n$ but the averaging step ($\bar{d} < 1$) that it relies on
is false for general graphs---see Act~IX.  The irony has a second
layer.]}
\end{claudebox}

\pivot{The layer switch lands. Eight hours of sparsification-layer
  attacks are bypassed by an elementary combinatorial proof discovered
  in 15~minutes. The proof uses three undergraduate-level facts:
  Tur\'an's theorem, the PSD trace bound, and the pigeonhole
  principle. The coaching did not supply mathematical content---it
  supplied \emph{questions} that forced layer enumeration.}

\begin{joebox}
It's so cool that this is the same basic solution we have used to
overcome continual shoring up of bad design in futon3, and also the
same solution I've used with Codex just now by getting it to spot
syntax errors rather than depending on me to do it.
\end{joebox}

\begin{claudebox}[title={Claude --- The meta-pattern}]
The diagnostic question is always the same: ``who finds this easy?''
If the answer is ``someone other than the entity currently
struggling,'' you're in the wrong layer.
\end{claudebox}

\pivot{The layer-switching pattern is recognized as fractal: it
  appears in proof strategy (Problem~6), in software design (futon3),
  and in task allocation (Codex as syntax checker). The common
  diagnostic: ask who would find the task trivial.}

%% ============================================================
\section*{Act VIII: The Monograph}
%% ============================================================

\begin{joebox}
In addition to the PAR I think it would be good to look through the
git log on futon6 and create a ``making of'' summary note.
\end{joebox}

\begin{joebox}
Also in terms of ``what we've learned''---in the making-of I think we
could add something about the relevance of this pattern to agent
teaming (further work in futon3c). Maybe this even goes back to the
work in futon2 ants---i.e.\ we are exploring a domain, bringing back
relevant information.
\end{joebox}

\begin{joebox}
I think the key thing you could help with now is looking through
\texttt{history.jsonl} for good quotes for Part~III.
\end{joebox}

\pivot{The sprint becomes its own document. The recursive
  structure---a proof sprint whose Part~III records the prompts that
  shaped Part~II---closes the loop between process and product.}

%% ============================================================
\section*{Act IX: The Continuation Cycles (Problems 4 and 6)}
%% ============================================================

The monograph was written during the sprint, not after it. The
sprint continued. Problems~4 and~6 entered multi-cycle proof
engineering phases that lasted days beyond the initial 48-hour
window---each cycle a dispatch, handoff, verification, and
reassessment. These cycles are the sprint's methodology running
at sustained pace rather than compressed urgency.

\subsection*{Problem 4: From Wrong Proof to Algebraic Engineering}

\begin{claudebox}[title={Claude --- Initial draft (Feb 11)}]
Proof by concavity of $1/\Phi_n$ in cumulant coordinates.
Since free cumulants are additive under $\boxplus$, Jensen's
inequality gives $1/\Phi_n(p \boxplus q) \ge 1/\Phi_n(p) +
1/\Phi_n(q)$.
\end{claudebox}

\pivot{The proof is wrong. $1/\Phi_n$ is superadditive in
  cumulant space WITHOUT being convex---the Hessian is indefinite.
  35,000 numerical trials confirm the conjecture but the argument
  is structurally broken. Numerical verification caught the
  conjecture but hid the proof error.}

\begin{claudebox}[title={Claude --- Key identity (Feb 12, commit \texttt{03c1f8d})}]
$\Phi_4(p) \cdot \operatorname{disc}(p)
  = -4(a_2^2 + 12a_4)(2a_2^3 - 8a_2 a_4 + 9a_3^2)$.
This converts the inequality to: prove a rational function's
numerator is non-negative on a semi-algebraic domain.
\end{claudebox}

\pivot{The first layer switch for Problem~4. Instead of hoping for
  a clever inequality (concavity, Schur-convexity, Cauchy--Schwarz),
  the problem is reduced to computational algebra: case
  decomposition by symmetry subspaces, resultant elimination,
  sign-counting. The identity itself is a publishable result---a
  finite analogue of Stam's inequality.}

\begin{claudebox}[title={Claude --- 3-piece Cauchy--Schwarz (commit \texttt{269fddd})}]
BREAKTHROUGH: the surplus decomposes into three pieces $T_1 + T_2
+ R$ where $T_1 \le 0$ (proved), and $T_2, R$ have
mutual-compensation structure. When $T_2 < 0$, $R$ compensates.
This reduces the full $n = 4$ proof to a degree-6 polynomial
inequality: $K_{T2R} \ge 0$.
\end{claudebox}

\pivot{A second layer switch within the algebraic layer.
  Symmetry-stratified elimination proved Cases~1, 2, 3a, 3b
  (resultant chains, 0.2--30 seconds each). Case~3c (generic, 4D)
  was handed to Codex with PHCpack. Seven SOS scripts proved that
  Positivstellensatz certificates are structurally impossible---the
  SOS cone misses the feasible set. The failure is a theorem, not a
  dead end: it rules out the entire SOS technique family.}

\subsection*{Problem 6: When Averaging Fails}

\begin{claudebox}[title={Claude --- Codex Cycle~7 (commit \texttt{a7b0e3e})}]
The Barrier Maintenance Invariant is \textbf{falsified}. 12
base-suite steps have $\bar{d} \ge 1$ (worst: 1.739, Reg\_100\_d10,
$\varepsilon = 0.5$, $t = 16$). The pigeonhole argument
($\bar{d} < 1 \Rightarrow \exists v$ with $\|Y_t(v)\| < 1$)
cannot close the construction.
\end{claudebox}

\pivot{The most dramatic moment in the continuation cycles. The
  averaging argument that the elementary proof relied on---the very
  argument whose discovery was the Act~VII breakthrough---turns out
  to be \emph{false} for general graphs. $\bar{d}_t < 1$ holds for
  $K_n$ but not universally. The construction still works (0~skips
  in 1,111 runs) because leverage-ordered vertices have small
  \emph{individual} contributions even when the average exceeds~1.
  The gap shifts from an averaging statement to a vertex-level
  feasibility statement: the \textbf{No-Skip Conjecture}.}

\begin{joebox}
I have engaged Codex in a systematic verification cycle on
Problem~6. Seven cycles so far. Each cycle narrows the gap: the
construction still works in every test---zero skips, zero
failures---but the proof keeps slipping. The trajectory is: method
wiring library $\to$ leverage threshold $\to$ barrier greedy
$\to$ BMI falsified $\to$ No-Skip Conjecture. At each stage, what
we thought was the gap turns out to be something more specific.
\end{joebox}

\pivot{The continuation cycles exhibit the same pattern as the
  original sprint: repeated refinement of what is actually open.
  The lemma that was GPL-H became BMI became the No-Skip
  Conjecture. Each reformulation is a genuine narrowing, not a
  retreat. The ``method wiring library'' from Cycle~1 (ten
  techniques with typed wiring diagrams) prevented commitment to
  any single approach before the landscape was mapped---the
  pre-proof infrastructure that Part~IV's Section~6 proposes as a
  design pattern.}

\subsection*{The Exhaustion-as-Theorem Pattern}

\begin{claudebox}[title={Claude --- Six techniques, one wall}]
All six subsample-and-concentrate techniques hit the same
quantitative wall: spectral contribution scales as $q^2$ while
set size scales as $q$. Trace/Markov: sublinear. Star domination:
$O(\varepsilon/\log n)$. Decoupling + MSS: $O(\varepsilon^2)$.
Greedy: $O(\varepsilon)$. Rank spreading: $O(\varepsilon^2)$.
The wall is fundamental to the technique family, not an artifact
of any one approach.
\end{claudebox}

\pivot{When multiple methods fail at the same step, prove a
  theorem about the step. This is the cross-problem pattern
  identified in Part~IV (Section~5) now demonstrated in the
  continuation: the exhaustion of a technique family produces a
  structural understanding that redirects effort. For Problem~6,
  it redirected from ``adapt edge sparsification'' (where every
  method hits the quadratic-vs-linear wall) to ``invent a new
  vertex-level argument'' (the leverage-ordered barrier greedy).
  For Problem~4, it redirected from SOS certification (structurally
  impossible) to resultant elimination (feasible and fast).}

%% ============================================================
\section*{Act X: The Gauntlet Connection}
%% ============================================================

\begin{joebox}
Also in terms of ``what we've learned''---in the making-of I think we
could add something about the relevance of this pattern to agent
teaming (further work in futon3c).
\end{joebox}

The sprint and its continuation are a slow-motion demonstration of
the infrastructure that the \texttt{futon3c} peripheral gauntlet
(M-peripheral-gauntlet) proposes to build. Every placental function
that the gauntlet enumerates was performed by a human during the
sprint:

\begin{description}
\item[Sensory gating.] Joe chose which problems to look at, which
  Codex outputs to read, which Claude sessions to trust. Gate~1
  (umwelt) would make this an agent capability.

\item[Belief correction.] ``That's replacing an overclaim with
  weasel words.'' ``I thought \#6 and \#7 were proved so I'm glad
  I asked!'' Gate~4 (AIF as environment) would make confidence
  state visible to agents without human narration.

\item[Policy selection.] ``Think out of the box---what kind of
  problem is this?'' The coaching intervention is a human-supplied
  policy switch. Gate~4 (AIF modeline) would let the agent perceive
  its own stuckness and trigger layer enumeration autonomously.

\item[Inter-agent routing.] ``I have two Codex research assistants
  working for you.'' Joe manually coordinated three concurrent
  processes, hitting OOM limits. Gate~0 (arena) and Gate~3
  (co-presence) would make agent activity structurally visible.

\item[Stall detection.] ``Codex is still after 53~minutes hard at
  work\ldots\ I will give it five more minutes and then say pencils
  down.'' Tickle---the watchdog agent proposed in the gauntlet---is
  exactly this function automated: detect stall, page the agent,
  escalate to human if the page fails.

\item[Confidence calibration.] ``Problem~6 has not brought out the
  best in Claude.'' The human's morning-after assessment that the
  gap-filling missions were running without valid confidence signals.
  Gate~5 (modeline persistence) would carry this calibration across
  sessions.

\item[Discovery surfacing.] ``It's so cool that this is the same
  basic solution we have used to overcome continual shoring up of
  bad design in futon3.'' Gate~7 (teaching inversion) would
  structure this insight---the cross-domain analogy between proof
  strategy and software design---as a discoverable pattern rather
  than a conversational aside.
\end{description}

The continuation cycles add a specific design insight: the
\textbf{($\text{layer}, \text{status}$) stationarity monitor}
proposed in Part~IV (Section~\ref{sec:learning}) \emph{is} the
proof-domain instance of Tickle. Problem~6's failed phase (six
dispatch-and-fail cycles over eight hours, all targeting the
sparsification layer) has the same $(\text{layer}, \text{status})$
signature as a stalled coding agent repeating the same approach:
stripes in the spacetime diagram. The monitor that detects
stationarity and triggers a reflect hop is Tickle for proofs.
The monitor that detects agent silence on IRC and pages it awake
is Tickle for coordination. Same pattern, same gate, different
timescale.

\pivot{The connection between the proof sprint and the gauntlet is
  not metaphorical. The sprint is evidence for the gauntlet: it
  demonstrates what autonomous multi-agent operation looks like when
  the infrastructure doesn't exist, and therefore what the
  infrastructure must provide. Every human intervention documented
  in this Part~III is a placental function. Every pivot annotation
  is a moment where that function transferred knowledge. The
  gauntlet's measure of success is that the pivots happen without
  the human---not because the human is excluded, but because the
  infrastructure carries the function. When that works, the human
  converges to the slow-timescale preference layer: choosing which
  problems to attempt, which proofs to trust, which discoveries to
  pursue. Everything else---stall detection, layer enumeration,
  confidence calibration, co-presence, modeline persistence---is
  infrastructure.}
