\section{Problem 8: Lagrangian Smoothing of 4-Valent Polyhedral Surfaces}

\subsection*{Problem statement}
If every vertex of a polyhedral Lagrangian surface in $(\mathbb R^4,\omega)$ is 4-valent, must the surface admit a Lagrangian smoothing through Hamiltonian isotopy?

\subsection*{Answer}
Yes.

\subsection*{Current status}
\phantomsection\label{sn:p8}
\statusnote{Current draft treats the geometric argument as closed, with unified
repair checks validating the main algebraic/maslov components. Remaining QC
work is ledger hygiene: synchronize these repairs with the canonical
node-level verifier record.}

\subsection*{Annotated proof sketch}
\begin{enumerate}[leftmargin=1.5em]
\item Analyze a 4-valent vertex: edge vectors span $\mathbb R^4$, forcing a symplectic splitting into two 2D factors.
\item Write the local model as a product of two planar corners and smooth each corner separately.
\item Check Lagrangian condition factorwise (product of isotropic curves in 2D symplectic factors).
\item Smooth remaining edge creases via exact-graph interpolation and glue local constructions by disjoint supports.
\item Promote to Hamiltonian isotopy using exactness/flux-vanishing in local models and composition closure of compactly supported Hamiltonian isotopies.
\end{enumerate}

\subsection*{Background and prerequisites}
\textbf{Field:} Symplectic Geometry / Lagrangian Topology.\\
\textbf{What you need:} Symplectic manifolds, Lagrangian submanifolds, Hamiltonian isotopy, and Weinstein neighborhood theorems. The proof uses only local symplectic techniques (no Floer theory).\\
\textbf{Way in:} McDuff--Salamon, \emph{Introduction to Symplectic Topology} (OUP, 3rd ed., 2017)---the standard graduate textbook covering all prerequisites.

\subsection*{Selected citations}
\begin{itemize}[leftmargin=1.5em]
\item Weinstein neighborhood theorem source paper: \url{https://www.sciencedirect.com/science/article/pii/000187087190005X}
\item McDuff--Salamon textbook page: \url{https://global.oup.com/academic/product/introduction-to-symplectic-topology-9780198794899}
\item Symplectic manifold definition: \url{https://planetmath.org/symplecticmanifold}
\item Lagrangian submanifold definition: \url{https://planetmath.org/lagrangiansubmanifold}
\end{itemize}

\clearpage
