\section{Problem 9: Polynomial Detection of Rank-1 Scaling for Quadrifocal Tensors}

\subsection*{Problem statement}
Given generic camera matrices and quadrifocal tensors $Q^{(\alpha\beta\gamma\delta)}$, construct a polynomial map $F$ of degree bounded independently of $n$ that vanishes exactly on rank-1 separable scaling tensors $\lambda_{\alpha\beta\gamma\delta}=u_\alpha v_\beta w_\gamma x_\delta$.

\subsection*{Answer}
Yes: one can use degree-3 determinant constraints (all relevant $3\times 3$ minors).

\subsection*{Current status}
\phantomsection\label{sn:p9}
\statusnote{Forward and witness checks are strong, but full closure still hinges
on a formal universal converse argument (all non-rank-1 \(\lambda\), not only
tested families). Treat as partial until that algebraic universality step is
written cleanly into the proof chain.}

\subsection*{Annotated proof sketch}
\begin{enumerate}[leftmargin=1.5em]
\item For fixed $(\gamma,\delta,k,\ell)$, the determinant pairing defines an alternating bilinear form of rank $2$ on $\mathbb R^4$, so all induced $3\times 3$ minors vanish.
\item If $\lambda$ is rank-1 separable, Hadamard-diagonal scaling preserves the rank-$\le 2$ property, hence all these minors vanish.
\item Conversely, vanishing of all minors across the three matricization patterns forces each matricization rank to be $1$, and compatibility implies full tensor separability.
\item Collect all such minors into $F$; each coordinate has degree $3$ and no dependence on camera parameters.
\end{enumerate}

\subsection*{Background and prerequisites}
\textbf{Field:} Algebraic Geometry / Computer Vision (Multiview Geometry).\\
\textbf{What you need:} Tensor algebra (rank, matricizations, Segre varieties), determinantal varieties, and the basics of multiview geometry (camera matrices, multi-focal tensors). The algebraic geometry is classical; no scheme theory required.\\
\textbf{Way in:} Hartley--Zisserman, \emph{Multiple View Geometry in Computer Vision} (Cambridge, 2nd ed.) for the applied setting; Landsberg, \emph{Tensors: Geometry and Applications} (AMS, 2012) for the algebraic underpinnings.

\subsection*{Selected citations}
\begin{itemize}[leftmargin=1.5em]
\item Segre embedding (rank-1 tensor variety): \url{https://planetmath.org/segreembedding}
\item Determinantal varieties: \url{https://planetmath.org/determinantalvariety}
\item Tensor rank definition: \url{https://planetmath.org/tensorrank}
\item Multiple-view geometry reference text: \url{https://www.robots.ox.ac.uk/~vgg/hzbook/}
\end{itemize}

\clearpage
